### 2021-08-06 manuscript/manuscript-speed-accuracy.tex

\PaperTitle{A meta-analysis of bioinformatics software benchmarks reveals major influences on software accuracy} 
%Analysis of sixty software benchmarks shows the benefits of good software practice 
%Assessing the state of the bioinformatic software landscape with a meta-analysis of benchmarks
%Sustained software development, not citation metrics, is indicative of accurate bioinformatic software 
%

@@

PPG is supported by a Rutherford Discovery Fellowship,
administered by the Royal Society Te Ap\=arangi, 
PPG, AG and MB acknowledge support from a Data Science Programmes grant
(UOAX1932).

>>>>

\PaperTitle{Sustained software development, not number of citations or journal choice, is indicative of accurate bioinformatic software}

%1 A meta-analysis of bioinformatics software benchmarks reveals major influences on software accuracy
%2 Analysis of sixty software benchmarks shows the benefits of good software practice 
%3 Assessing the state of the bioinformatic software landscape with a meta-analysis of benchmarks
%4 Sustained software development, not citation metrics, is indicative of accurate bioinformatic software 
%

@@

PPG is supported by a Rutherford Discovery Fellowship,
administered by the Royal Society Te Ap\=arangi, 
PPG, AG and MAB acknowledge support from a Data Science Programmes grant
(UOAX1932).
